CAT-DWAM, A Question Answering System

### 2011-05-07 paper/paper.tex
experiment
comment table
paper

\begin{figure}
 \label{diagram}
 \begin{center}
  \begin{tikzpicture}[node distance=2.5cm, auto, >=stealth]
   % nodes
   \node[data] (Q)                                      {Question};
   \node[process] (ch) [below of=Q]                     {Chunker};
   \node[null] (xx) [right of=ch]                     {};
   \node[data] (docs) [right of= xx]                     {Documents};
   \node[process] (fil) [below of=ch]                     {Filter};
   \node[process] (a2) [below of=fil]                    {Answer Evaluator};
   \node[process] (a1) [left of=a2]                     {Answer Evaluator};
   \node[process] (a3) [right of=a2]                    {Answer Evaluator};
   \node[machine] (as) [below of=a2]                    {Score aggregator};
   \node[data] (A) [below of=as]                        {Answer};

@@

We implemented a system to compare the question and answer against the proposed
document in two ways:  one, with a na\"ive diffing algorithm that simply seeks
out the longest indentical sequence, and one by implementing the Smith-Waterman
local alignment
algorithm.\footnote{\url{http://en.wikipedia.org/wiki/Smith-Waterman_algorithm}}
We also implemented a system to attempt to re-write questions, discussed below,
and applied these same techniques to the re-written question

@@

1 if the candidate answer is immmediately followed by a comma, period, quotation
marks, semicolon, or exclamation mark, and 0 otherwise. This is a good heuristic
by which to rank candidate answers since it retrieves a property from the
context where the answer appears in the document.

@@

\subsubsection{Measurement Units or Matching Type Filters}
% Tom
For quantity-type answer candidates, we used simple regular expressions to
extract the proceeding and preceeding space-delimited phrases. This is quite
close to a lay definition of ``word''; for the answer candidate ``about 350
km/h'', the phrases ``about'' and ``km/h'' would be extracted as units. We
extracted the units from the training corpus.

For test answers, we searched the context of the answer for colocated units
matching what we found in the training corpus. We returned a score of 1 if there
was a unit and a score of 0 if there wasn't.

@@

%We tried these classifiers separately rather than 
%We ended using just the SRDA classifier since the others were throwing memory errors.
The implementation of these classifiers in mlpy required too much memory for
us to run the models on the all of the candidate answers. We used two main approaches
to solve these problems.
\begin{itemize}
\item We used SRDA because it seemed to handle the largest sample size.
\item We created a decision list from some of our answer evaluators. We ran the anwers
through this decision list before sending them to the SRDA learning algorithm.
\end{itemize}

\subsection{Other choices}
Since the system was taking too long to run we made several choices in order
to get meaningful results on which to report on. We decided to specifically analyze
the ``Where'' questions since there were 28 of them, which seemed like an appropriate
amount to train on. We ran into some prombles with some of these questions, so we
actually only used 24 of these questions.

\section{Results}
\begin{table}
\begin{tabular}{lcc}
%\toprule
\cmidrule{2-3}
                     & Number correct & Mean recipricol rank\\
\cmidrule{2-3}
Punctuation location &                &                     \\
Novelty factor       &                &                     \\
Both                 &                &                     \\
\cmidrule{2-3}
%\bottomrule
\end{tabular}
\caption{\label{tab:results}Results of our system on ``Where''-type questions. }
\end{table}
% we need:
% the output file of answers produced by our system for the questions
% from the development corpus
% an evaluation using the Mean Reciprocal Rank Evaulation Measure)
% an analysis of the system's performance on questions of the
% development corpus
   % what worked?
   % what didn't work?
   % which component was strongest/weakest?
   % how does our system compare to the baseline?
% responses from our system for test set released on Wednesday
   % we also need to submit this file

@@

\subsection{Graphical Methods}

\subsection{Best Run Results}

@@

>>>>

\begin{figure}
 \label{diagram}
 \begin{center}
  \begin{tikzpicture}[node distance=2.5cm, auto, >=stealth]
   % nodes
   \node[data] (Q)                                      {Question};
   \node[process] (ch) [below of=Q]                     {Chunker};
   \node[null] (xx) [right of=ch]                     {};
   \node[data] (docs) [right of= xx]                     {Documents};
   \node[process] (fil) [below of=ch]                     {Filter};
   \node[process] (a2) [below of=fil]                    {Answer Evaluator};
   \node[process] (a1) [left of=a2]                     {Answer Evaluator};
   \node[process] (a3) [right of=a2]                    {Answer Evaluator};
   \node[machine] (as) [below of=a2]                    {Score Aggregator};
   \node[data] (A) [below of=as]                        {Answer};

@@

We implemented a system to compare the question and answer against the proposed
document in two ways:  one, with a na\"ive diffing algorithm that simply seeks
out the longest identical sequence, and one by implementing the Smith-Waterman
local alignment
algorithm.\footnote{\url{http://en.wikipedia.org/wiki/Smith-Waterman_algorithm}}
We also implemented a system to attempt to re-write questions, discussed below,
and applied these same techniques to the re-written question

@@

1 if the candidate answer is immediately followed by a comma, period, quotation
marks, semicolon, or exclamation mark, and 0 otherwise. This is a good heuristic
by which to rank candidate answers since it retrieves a property from the
context where the answer appears in the document.

@@

\subsubsection{Measurement Units or Matching Type Filters}
% Tom
For quantity-type answer candidates, we used simple regular expressions to
extract the proceeding and preceding space-delimited phrases. This is quite
close to a lay definition of ``word''; for the answer candidate ``about 350
km/h'', the phrases ``about'' and ``km/h'' would be extracted as units. We
extracted the units from the training corpus.

For test answers, we searched the context of the answer for co-located units
matching what we found in the training corpus. We returned a score of 1 if there
was a unit and a score of 0 if there wasn't.

@@

%We tried these classifiers separately rather than 
%We ended using just the SRDA classifier since the others were throwing memory errors.
The implementation of these classifiers in mlpy required too much memory for
us to run the models on the all of the candidate answers. We used two main approaches
to solve these problems.
\begin{itemize}
\item We used SRDA because it seemed to handle the largest sample size.
\item We created a decision list from some of our answer evaluators. We ran the
answers through this decision list before sending them to the SRDA learning
algorithm.
\end{itemize}

\subsection{Other choices}
Since the system was taking too long to run we made several choices in order
to get meaningful results on which to report on. We decided to specifically analyze
the ``Where'' questions since there were 28 of them, which seemed like an appropriate
amount to train on. We ran into some problems with some of these questions, so we
actually only used 24 of these questions.

\section{Results}
\begin{table}
\begin{tabular}{llcc}
%\toprule
\cmidrule{2-4}
               &       & Number correct & Mean reciprocal rank\\
\cmidrule{2-4}
9 Training&Punctuation location &   0            &      0              \\
questions&Novelty factor       &    0           &       0             \\
&Both                 &             0  &                0    \\
\cmidrule{2-4}
24 Training&Punctuation location &                &                     \\
questions&Novelty factor       &                &                     \\
&Both                 &                &                     \\
\cmidrule{2-4}
%\bottomrule
\end{tabular}
\caption{\label{tab:results}Results of our system on ``Where''-type questions. }
\end{table}
% we need:
% the output file of answers produced by our system for the questions
% from the development corpus
% an evaluation using the Mean Reciprocal Rank Evaulation Measure)
% an analysis of the system's performance on questions of the
% development corpus
   % what worked?
   % what didn't work?
   % which component was strongest/weakest?
   % how does our system compare to the baseline?
% responses from our system for test set released on Wednesday
   % we also need to submit this file

@@

@@

Unfortunately, our system took much longer than expected to run, so we were
only able to run it on very small input sets, which produced, well, awful
results.

This prevents us from drawing conclusions about the efficacy of the methods we
used except for the following:

SRDA, at least in this implementation, is probably too resource-intensive for
use in this sort of context, where we generate tens of thousands of potential
answer candidates and ascribe to them many different features.

Either we got unlucky (with this small sample size, it is quite likely), or
SRDA doesn't perform well with small training sets.  This is to be expected,
but is still disheartening.

Had we been able to run the system on a deeper training set and over more
questions in the test set (and, ideally, over a validation set to tweak the
values of various components, particularly that of the sequence aligner), we
would have liked to make conclusions about the efficacy of the various
techniques, particularly sequence alignment, which we believe has some promise
that the NLP community seems to have overlooked.  Of course, it is not a very
fast method either on these datasets, so it may also be too slow for common use.
